\documentclass[12pt,a4paper]{article}
%-----------------------PACKAGES-----------------------%
\usepackage[top=1in,bottom=1in,left=0.5in,right=0.5in]{geometry}
\usepackage{graphicx}
\usepackage{array}
\usepackage{xcolor}
\usepackage{adjustbox}
\usepackage{titlesec}
\usepackage{svg}
\usepackage{lettrine}

%-----------------------TABLES ALIGNEMNET-----------------------%

%-----------------------TITLE DOCUMENT-----------------------%
\begin{document}
	\input{Titlepage}
 
 \clearpage
%-----------------------TABLE OF CONTENT-----------------------% 
% \tableofcontents
% \clearpage
%-----------------------TABLE OF CONTENT-----------------------% 
\section{Plexaar  assigning premission and roles apis:}
Today,I have tested the plexaar apis.I will share the postman collection.These are the apis in which i faced the issue.
% \newline\textbf{Country:}
% \begin{itemize}
%     \item 
% \end{itemize}
% \newline\textbf{Currencies:}
% \begin{itemize}
%     \item 
% \end{itemize}
% \newline\textbf{Language:}
% \begin{itemize}
%     \item 
% \end{itemize}
\newline\textbf{Customer:}
\begin{itemize}
    \item Customer is not creating.
\end{itemize}
\newline\textbf{eventTypes:}
\begin{itemize}
    \item \textbf{addNewEvent:} api it is not working.
\end{itemize}
 \textbf{Premission:}
\begin{itemize}
    \item \textbf{getAllPremission} api it is not working.
    \item \textbf{updatePremission} api is not working.
    \item \textbf{removePremisison} api is not working.
\end{itemize}
\textbf{eventPremission:}
\begin{itemize}
\item The \textbf{eventTypes:} api is not working so i can not set premission against these events.
\end{itemize}
\textbf{Roles:}
\begin{itemize}
    \item \textbf{addNewRole} This api is working but other apis are not working.
\end{itemize}
\textbf{RoleEvents:}
\begin{itemize}
    \item It need event Id in order to give role but our event type collection is not working.
\end{itemize}
\textbf{UserRoles:}
\begin{itemize}
    \item \textbf{asignUserRole} It is creating role but other api is not working.
\end{itemize}
\section{Admin site sms template}
Waiting response from developer side as pervious issue was not resolved and now it is in progress.
\section{Chat and Call module}
It still need to be tested.

\end{document}